---
title: "Evaluation"
output: html_document
---

```{r}
library(psych)
source('util.R')
source('survey_696322_R_syntax_file.R')
data <- data[,c(2:length(data))]
```

```{r}
summary(data$Q002)
data <- data[data$Q002 < 30,]
hist(data$Q002, main = "Anzahl erwerbstatiger Semsester")
```

someone had 333 semesters -> remove

```{r}
summary(data$Q003)
hist(data$Q003, main = "Anzahl Praktika")
```

```{r}
summary(data$Q013)
boxplot(data$Q013, main = "Alter")
```


```{r}
summary(data$Q015)
hist(data$Q015, main = "Anzahl Semester")
```

```{r}
plot(data$Q016, main = "Haufigkeit akademischer Grade")
levels(data$Q016)[3] <- levels(data$Q016)[2]
```

No respondent was a doctor, so we remove this category.


```{r}
data["AnteilErwerbssemester"] <- data$Q002 / data$Q015
paste("Students with working semesters > 0 but semesters = 0: ", sum(is.infinite(data$AnteilErwerbssemester)))
data <- data[!is.infinite(data$AnteilErwerbssemester),]
data[is.nan(data$AnteilErwerbssemester),]$AnteilErwerbssemester <- 0
data[data$AnteilErwerbssemester > 1,]$AnteilErwerbssemester <- 1
```

someone had Erwerbssemester > 0 while Semester = 0, which is impossible -> remove

```{r}
data["PraktikaProSemester"] <- data$Q003 / data$Q015
paste("Students with internships > 0 but semesters = 0: ", sum(is.infinite(data$AnteilErwerbssemester)))
data[is.infinite(data$PraktikaProSemester),]$PraktikaProSemester <- 1
data[is.nan(data$PraktikaProSemester),]$PraktikaProSemester <- 0
data[data$PraktikaProSemester > 1,]$PraktikaProSemester <- 1
```


Dependent Variable
---

Explanations in karriereerwartung.Rmd

```{r}
pca.data <- data[,c("Q001_SQ003", "Q001_SQ005")]
indx <- sapply(pca.data, is.factor)
pca.data[indx] <- lapply(pca.data[indx], as.numeric)
pca.result <- principal(pca.data, nfactors = 1, scores = TRUE)
erfolg.scores <- pca.result$scores[,'PC1']
data["Erfolg"] <- erfolg.scores
```



Hypothesis 1
---

More work during university -> higher aspiration for career success

### `Erwerbstätigkeit` index

```{r}
erwerb.data <- data[,c("AnteilErwerbssemester", "PraktikaProSemester")]
boxplot(list(data$AnteilErwerbssemester, data$PraktikaProSemester))
```

```{r}
alpha(erwerb.data)
KMO(erwerb.data)
```

Anteil Erwerbssemester and Praktika pro Semester are not reliable measures (alpha = 0.11), KMO = 0.5 -> therefore PCA not really fitting

We decide to test the hypothesis for both individually -> no `Erwerbstätigkeit` index

### Test

Does the amount of semesters in which a student worked affect the aspiration for career success?

```{r}
plot(data$Q002, data$Erfolg, xlab = "Anzahl erwerbstätige Semester", ylab = "Erfolgserwartung")
```

The plot seems to show a slight negative correlation. We use a linear regression to see if this is significant. Our hypotheses using a significance level of $\alpha=0.05$ are:

* $H_0$: The regression coefficient of the variable `Anzahl erwerbstätige Semester` is 0. $\beta_{Anzahl erwerbstätige Semester} = 0$
* $H_A$: The regression coefficient of the variable `Anzahl erwerbstätige Semester` is different from 0. $\beta_{Anzahl erwerbstätige Semester} \neq 0$

```{r}
lm.result <- lm(Erfolg ~ Q002, data)
summary(lm.result)
```

The result of the linear regression using ordinary least squares is that  $\beta_{Anzahl erwerbstätige Semester}$ is not significantly different from 0, as the corresponding p-value is 0.124 > $\alpha$. Therefore, there is no evidence that the aspiration for career sucess is dependent upon the amount of semesters in which a student worked.

We still need to look at a few plots of the linear model to see if it is useful for our dataset.

```{r}
plot(lm.result)
```

quantile-quantile not really god, residual plot ok

```{r}
plot(data$Q003, data$Erfolg, xlab = "Anzahl Praktika", ylab = "Erfolgserwartung")
```


```{r}
lm.result <- lm(Erfolg ~ Q003, data)
summary(lm.result)
```

significant: the more internships, the less Erfolg aspiration -> our hypothesis is false

```{r}
plot(lm.result)
```

quantile-quantile not really god, residual plot ok

Hypothesis 2
---

higher support of parents -> higher aspiration for career success

```{r}
support.data <- data[,c("Q004_SQ001", "Q004_SQ002", "Q004_SQ003", "Q004_SQ004", "Q004_SQ005", "Q004_SQ006", "Q004_SQ007")]
support.data <- factors.as.numeric(support.data)
alpha(support.data)
KMO(support.data)
```

good alpha and KMO -> PCA
```{r}
support.data <- support.data[-1]
support.names <- c("Books", "Fees", "Travel", "Food", "Allowance", "Expenses")
alpha(support.data)
KMO(support.data)
```



```{r}
pca.result <- principal(support.data, nfactors = 1, scores = TRUE)
support.scores <- pca.result$scores[,'PC1']
data["HilfeEltern"] <- support.scores
plot(pca.result$value, type = 'b', main = 'Screeplot')
```

```{r}
barplot(pca.result$loadings[,1], names.arg = support.names, main = "Item loadings on parental support factor", ylab = "Loading", xlab = "Items")
```

```{r}
hist(data$HilfeEltern)
```

```{r}
plot(data$HilfeEltern, data$Erfolg, xlab = "Parental support", ylab = "Aspiration for career success")
```


```{r}
lm.result <- lm(Erfolg ~ HilfeEltern, data)
plot(lm.result)
```

quantile and residual plots suggest that the linear model fits the data

```{r}
summary(lm.result)
```

As the p-value is lower than $\alpha$, we know that $\beta_{parental support}$ is significantly different from 0. As the estimate of $\beta_{parental support}$ is positive, we know that more support of parents leads to a higher aspiration for career success.

Hypothesis 3
---

higher cost of living -> higher aspiration for career success

```{r}
plot(data$Q005)
```

ordinal scale

```{r}
boxplot(Erfolg ~ Q005, data)
```

medians do not seem to differ a lot

since only 351-600 is normally distributed, we need to use a robust test -> Kruskall-Wallis test:

```{r}
kruskal.test(Erfolg ~ Q005, data)
```

insignificant -> median is not different in groups -> no evidence that aspiration for career success is dependent on cost of living

Hypothesis 4
---

higher social assistance -> less aspiration for career success

```{r}
plot(data$Q006)
```

ordinal scale

```{r}
levels(data$Q006)[4] <- levels(data$Q006)[3]
levels(data$Q006)[3] <- "über 250€"
```

too few occurences for the last two categories, so we combine them

```{r}
boxplot(Erfolg ~ Q006, data)
```

The median in category `0-100€` seems the be higher than the other medians. As the categories are not normally distributed, we use a Kruskall-Wallis test to investigate this.

```{r}
kruskal.test(Erfolg ~ Q006, data)
```

insignificant -> median is not different in groups -> no evidence that aspiration for career success is dependent on social assistance

Hypothesis 5
---

more grants -> higher aspiration for career success

```{r}
plot(data$Q007)
```

ordinal scale

```{r}
summary(data$Q007)
```

only four respondents receive grants -> too small sample

```{r}
levels(data$Q007)[4] <- levels(data$Q007)[2]
levels(data$Q007)[3] <- levels(data$Q007)[2]
levels(data$Q007)[2] <- "ja"
levels(data$Q007)[1] <- "nein"
```


convert into dichotomous variable: receive grant yes or no


```{r}
boxplot(Erfolg ~ Q007, data, main = "Leistungsstipendium erhalten")
```

There seems to be a significant difference in the medians. Apparently, students who receive grants have less aspiration for career success.

We use a statistical test to see if this holds up. Since both groups are not normally distributed, we need to use the robust Kruskall-Wallis test.

Our test hypotheses using a significance level $\alpha=0.05$ are:

* $H_0: \mu^{Erfolg}_{kein Leistungsstipendium} = \mu^{Erfolg}_{Leistungsstipendium erhalten}$
* $H_A: \mu^{Erfolg}_{kein Leistungsstipendium} \neq \mu^{Erfolg}_{Leistungsstipendium erhalten}$

```{r}
kruskal.test(Erfolg ~ Q007, data)
```

The p-value is 0.04, which is lower than our $\alpha$. Therefore, we can accept $H_A$. There is evidence that students who receive grants have significantly lower aspiration for career success.

Hypothesis 6
---

more available financial capital -> higher aspiration for career success

```{r}
plot(data$Q008)
```

ordinal scale

```{r}
levels(data$Q008)[5] <- levels(data$Q008)[4]
levels(data$Q008)[4] <- "über 1000€"
```

We see that only three observations fall into the `über 2000€` category. We therefore decided to combine this level with the `1001-2000€` level. The newly created level is simply called `über 1000`.

```{r}
boxplot(Erfolg ~ Q008, data)
```

medians do not seem to differ a lot

since no category is normally distributed, we need to use a robust test -> Kruskall-Wallis test:

```{r}
kruskal.test(Erfolg ~ Q008, data)
```

insignificant -> median is not different in groups -> no evidence that aspiration for career success is dependent on available financial capital

Hypothesis 7
---

better living -> higher aspiration for career success

```{r}
data$Q012 <- factor(data$Q012, levels=rev(levels(data$Q012)))
wohn.data <- data[,c("Q009", "Q010", "Q011", "Q012")]
wohn.data <- factors.as.numeric(wohn.data)
alpha(wohn.data[,1:2])
KMO(wohn.data)
```

$\alpha$ and KMO too low

Let's try individual hypotheses

```{r}
boxplot(Erfolg ~ Q009, data)
```


```{r}
summary.aov(aov(Erfolg ~ Q009, data))
```

significant -> housing affects aspiration for career success

all the following variables are insignificant

```{r}
boxplot(Erfolg ~ Q010, data)
```


```{r}
summary.aov(aov(Erfolg ~ Q010, data))
```

```{r}
boxplot(Erfolg ~ Q011, data)
```


```{r}
summary.aov(aov(Erfolg ~Q011, data))
```

```{r}
boxplot(Erfolg ~ Q012, data)
```


```{r}
summary.aov(aov(Erfolg ~ Q012, data))
```
