---
title: "Dependent Metric and Independent Categorical Variable Part 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this document, we want to answer the following research question:
The more financial capital a student has available, the higher is a student's aspiration for career success.

To answer this question, we need to load the data.

```{r}
library(psych)
data <- read.csv('survey_696322_R_data_file.csv')
data <- data[,c(3,5)]
indx <- sapply(data, is.factor)
data[indx] <- lapply(data[indx], as.numeric)
pca.result <- principal(data, nfactors = 1, scores = TRUE)
erfolg.scores <- pca.result$scores[,'PC1']
source('survey_696322_R_syntax_file.R')
data['erfolg'] <- erfolg.scores
```

Let's look at the `Kapital` variable indicating the available monthly financial capital.

```{r}
plot(data$Q008, xlab = "Kapital", ylab = "Frequency")
```

We see that only three observations fall into the `über 2000€` category. We therefore decided to combine this level with the `1001-2000€` level. The newly created level is simply called `über 1000`.

```{r}
levels(data$Q008)[5] <- levels(data$Q008)[4]
levels(data$Q008)[4] <- "über 1000€"
```

Now let's look at the summary statistics for the specific categories.

```{r}
describeBy(data$erfolg, group = data$Q008)
```

```{r}
boxplot(erfolg ~ Q008, data, ylab = "Erfolg scores", main = "Erfolg scores by Kapital")
```

We see in the above boxplot that the difference between the medians is rather minute. Additionally, we can see that the `Erfolg` scores are not normally distributed in the `0-200€`, `501-1000€` and `über 1000` categories.

Let's see if a statistical test comes to the same conclusion. Due to the above insights, we know that we need a robust test. We decide to use the Kruskal-Wallis test using a significance level $\alpha=0.05$ with the following hypotheses:

* $H_0$: $\mu^{Erfolg}_{0-200€} = \mu^{Erfolg}_{201-500€} = \mu^{Erfolg}_{501-1000€} = \mu^{Erfolg}_{über 1000€}$
* $H_A$: At least one $\mu$ is different

```{r}
kruskal.test(erfolg ~ Q008, data)
```

The Kruskall-Wallis test yields a p-value of roughly 0.4, which is higher than our $\alpha$. Therefore, we cannot reject $H_0$. We have no significant evidence of a difference in the means of the `Kapital` groups.
